\bf Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-15 appendix.qmd
Removed the whitespace

triangle_arrow_temp <- tibble(
  x = c(4 + 0.04, 0 - 0.06, 4 + 0.06),
  xend = c(0 + 0.04, 0 - 0.06, 0 + 0.06),
  y = c(0 - 0.04, 0 - 0.06, 0 + 0.06),
  yend = c(0 - 0.04, 3 - 0.06, 3 + 0.06)
)

@@

The layout a (@fig-pbmc-mse-umap) is generated from the hyper-parameters suggested by @chen2023, and the layout b (@fig-pbmc-mse-umap) is with suggested hyper-parameters by scDEED to be more accurate. The layout a and b contain $46$ and $83$ dubious cells respectively.

The log MSE vs binwidth ($a_1$) plot (@fig-pbmc-mse-umap) illustrates that our approach would suggest that scDEED is correct here, that layout b is more accurately reflecting the cluster structure in the PBMC data.

@@

# Combine the plots using the layout
(error_umap_plot_pbmc + nldr1c + nldr2c) +
  plot_layout(design = layout_design)
```

>>>>

# triangle_arrow_temp <- tibble(
#   x = c(4 + 0.04, 0 - 0.06, 4 + 0.06),
#   xend = c(0 + 0.04, 0 - 0.06, 0 + 0.06),
#   y = c(0 - 0.04, 0 - 0.06, 0 + 0.06),
#   yend = c(0 - 0.04, 3 - 0.06, 3 + 0.06)
# )

@@

@@

# Combine the plots using the layout
(error_umap_plot_pbmc + nldr1c + nldr2c) +
  plot_layout(design = layout_design)
```
The layout a (@fig-pbmc-mse-umap) is generated from the hyper-parameters suggested by @chen2024, and the layout b (@fig-pbmc-mse-umap) is with suggested hyper-parameters by scDEED to be more accurate. The layout a and b contain $46$ and $83$ dubious cells respectively.

The RMSE vs binwidth ($a_1$) plot (@fig-pbmc-mse-umap) illustrates that our approach would suggest that scDEED is correct here, that layout b is more accurately reflecting the cluster structure in the PBMC data.

### 2025-05-15 appendix.tex
Removed the whitespace

The layout a (Figure~\ref{fig-pbmc-mse-umap}) is generated from the
hyper-parameters suggested by \citet{chen2023}, and the layout b
(Figure~\ref{fig-pbmc-mse-umap}) is with suggested hyper-parameters by
scDEED to be more accurate. The layout a and b contain \(46\) and \(83\)
dubious cells respectively.

The log MSE vs binwidth (\(a_1\)) plot (Figure~\ref{fig-pbmc-mse-umap})
illustrates that our approach would suggest that scDEED is correct here,
that layout b is more accurately reflecting the cluster structure in the
PBMC data.

@@

>>>>

@@

The layout a (Figure~\ref{fig-pbmc-mse-umap}) is generated from the
hyper-parameters suggested by \citet{chen2024}, and the layout b
(Figure~\ref{fig-pbmc-mse-umap}) is with suggested hyper-parameters by
scDEED to be more accurate. The layout a and b contain \(46\) and \(83\)
dubious cells respectively.

The RMSE vs binwidth (\(a_1\)) plot (Figure~\ref{fig-pbmc-mse-umap})
illustrates that our approach would suggest that scDEED is correct here,
that layout b is more accurately reflecting the cluster structure in the
PBMC data.
